A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Improve environments

The \c{sys.call} option is not used a lot, only \SysCallEnvirPercent as a whole, and always with \c{sys.parent()} as argument.

@@

The \emph{glue} library is used to interpolate string litterals with variables, such as in \c{glue('My name is {name}.')} where \c{name} will be subtituted by its value. \emph{glue} makes it possible to define transformers that process those interpolated variables. They are built upon the \c{identity_transformer}, which uses \eval. The interpretation environment for \eval is often global here, as the string litterals are often used to print variabels at the top level.

@@

We finally look at the case where \c{envir} is not an environment, but a list, such as this \c{h2} function, defined inside function \c{adjCoef} in package \emph{actuar}.

\begin{lstlisting}
h2 <- function(x, y)
    eval(parse(text = fcall),
    envir = list(x = x, y = y),
    enclos = parent.frame(2))
\end{lstlisting}

>>>>

%The \c{sys.call} option is not used a lot, only \SysCallEnvirPercent as a whole, and always with \c{sys.parent()} as argument.

@@

The \emph{glue} library is used to interpolate string litterals with variables, such as in \c{glue('My name is \{name\}.')} where \c{name} will be subtituted by its value. \emph{glue} makes it possible to define transformers that process those interpolated variables. They are built upon the \c{identity_transformer}, which uses \eval. The interpretation environment for \eval is often global here, as the string litterals are often used to print variabels at the top level.

@@

\c{adjCoef} in package \emph{actuar} find the root of an equation defined by a function \c{h} whose arguments must be named \c{x} and \c{y}.
\c{h} is transformed into an auxiliary function \c{h2} that can be optimized. Here, the list used for \c{envir} ensures the correspondance between the textual arguments of \c{h} and the arguments of \c{h2}.

\begin{lstlisting}
sh <- substitute(h)
fcall <- paste(sh, "(x, y)")
...
h2 <- function(x, y)
    eval(parse(text = fcall),
    envir = list(x = x, y = y),
    enclos = parent.frame(2))
\end{lstlisting}
